\chameleon{}: Untangling Type Errors Through Interactive Visualization and Exploration

### 2022-12-12 sections/chameleon.tex
Numbering RQ

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, trim=0mm 10mm 0mm 0mm]{images/intro-compare.pdf}
    \caption{
        \textbf{\chameleon{} minimal output (with candidate expression cards and deduction step disabled)}. \chameleon{} identified the conflicting types for the function \texttt{a} and associated the relevant locations with each type. In addition, \chameleon{} leaves out the right-hand side of the declaration '\texttt{0}' and '\texttt{1}' because they are unrelated.
}
    \label{fig:compare}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, trim=0mm 10mm 0mm 0mm]{images/intro-compare-2.pdf}
    \caption{
        \textbf{\chameleon{} with type compare tool enabled}. \chameleon{} identified the conflicting types for the expression \texttt{u} and associated the relevant locations with each type. Compare the output with the traditional type error message in fig. \ref{fig:motivation-example}.
}
    \label{fig:compare}
\end{figure}

### 2022-12-12 sections/evaluation.tex
Numbering RQ

More specifically:
\begin{itemize}
    \item Do programmers prefer switching modes during debugging type errors?
    \item What are programmers' preferences among the three modes provided by \chameleon{} 2?
    \item How do programmers use the advanced features provided by \chameleon{} 2?

@@

The most striking feature of the data is that users tend to vary wildly in their use of the tool. Some users used the features extensively while others completed the tasks without actively exploring the given information. Based on this discrepancy, we divided the users into three groups:

@@

Another observation is when using the mode switching feature of \chameleon{}, we find presenting the starting mode and finishing mode of each task and each participant in a correlation matrix is very telling (Fig. \ref{fig:r4-mode-switching}). This observation suggests two characteristics of using multi-mode debugging tools. First, programmers are generally reluctant to switch modes (146/277 changing modes vs. 131/277 staying in the same mode). Second, when changing modes, programmers generally switch to the more informative modes instead of, the more concise ones.
\begin{figure}
    \centering
    \includegraphics[width=0.7\linewidth,trim=0mm 5mm 0mm 5mm,clip]{images/mode-switching.pdf}
    \caption{Study 2 mode switches by starting mode.  Users overwhelmingly switched to the more sophisticated interface mode.
        % The rows represent the finishing mode, columns starting modes.
    }
    \label{fig:r4-mode-switching}
\end{figure}

>>>>

More specifically:
\begin{itemize}
    \item \textbf{RQ2.1} How do programmers use the advanced features provided by \chameleon{} 2?
    \item \textbf{RQ2.2} Do programmers prefer switching modes during debugging type errors?
    \item  \textbf{RQ2.3} What are programmers' preferences among the three modes provided by \chameleon{} 2?

@@

\textbf{RQ2.1}. The most striking feature of the data is that users tend to vary wildly in their use of the tool. Some users used the features extensively, while others completed the tasks without actively exploring the given information. Based on this discrepancy, we divided the users into three groups:

@@

Another observation is when using the mode switching feature of \chameleon{}, we find presenting the starting mode and finishing mode of each task and each participant in a correlation matrix is very telling (Fig. \ref{fig:r4-mode-switching}). This observation suggests two characteristics of using multi-mode debugging tools. First, to answer \textbf{RQ2.2} programmers are generally reluctant to switch modes (146/277 changing modes vs. 131/277 staying in the same mode). Second, to answer \textbf{RQ2.3} when changing modes, programmers generally switch to the more informative modes instead of, the more concise ones.
\begin{figure}
    \centering
    \includegraphics[width=0.7\linewidth,trim=0mm 5mm 0mm 5mm,clip]{images/mode-switching.pdf}
    \caption{Study 2 mode switches by starting mode.  Users overwhelmingly switched to the more sophisticated interface mode.
        % The rows represent the finishing mode, columns starting modes.
    }
    \label{fig:r4-mode-switching}
\end{figure}
